Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-01 doc/tfp-2011/main.tex
experiments

@@

The following table shows execution times for various values of $N$
and our three different implementations: \of{Sequential}, \of{Cores}, and
\of{Network}. The purpose of this experiment is to measure the speedup
w.r.t. the sequential implementation. Therefore, all
computations are performed on the same machine, a 8 cores Intel Xeon
3.2 GHz running Debian Linux. The sequential implementation uses a
single core. The multi-core implementation uses the 8 cores of
the machine. The network implementation uses 8 workers running locally and
a master running on a remote machine (which incurs communication cost).

@@

% ICI

Here we demonstrate the potential of our library for our application
needs as mentioned in the introduction. In this case study,
we consider 80 challenging verification conditions
(VC) obtained from the Why platform~\cite{filliatre07cav}.  Each
VC is stored in a file, which is accessible over
NFS. The purpose of the experiment is to check the validity of each VC
using several automated provers (namely Alt-Ergo, Simplify, Z3 and CVC3),
which are all installed on each of the machines in use.

The master program proceeds by reading the file names, turning them
into tasks by multiplying them by the number of provers (more than
300 tasks in total).
Each worker in turn invokes the given prover on the given file, within
a timeout limit.
Each task completes with one of the four possible outcomes: \emph{valid},
\emph{unknown} (depending on
whether the VC is valid or undecided by the prover), 
\emph{timeout} and \emph{failure}.

The result of each computation is a pair denoting the status and the
time spent in the prover call. The master collects these results and
sums up the timings for each prover and each possible status.

\subsection{SMT Solvers}

As explained in Section~\ref{sec:SMT}, this benchmark consists of 80
verification conditions, each being checked by 4 different SMT
solvers. Each task is executed with a timeout limit of 1 minute.
Our computing
infrastructure for this experiment consists of 3 machines with 4, 8 and 8 cores
respectively. 
The figure below shows the total time in minutes spent by each prover
for each possible outcome.
\begin{center}
  \begin{tabular}{|r||r|r|r|r|}
    \hline
    prover   & valid & unknown & timeout & failure
    \\\hline\hline
    Alt-ergo & 406.0 & 3.0   &  11400.0 & 0.0       
    \\\hline
    Simplify &  0.5   & 0.4   &  1200.0 & 222.0   
    \\\hline
    Z3       & 80.7   & 0.0   &  1800.0 & 1695.0   
    \\\hline
    CVC3     & 303.0  & 82.7  &  4200.0 & 659.0   
    \\\hline
  \end{tabular}
\end{center}
These figures sum up to more than 6 hours if provers were executed
sequentially. However, using our library and our 3-machine
infrastructure, it completes in 22 minutes and 37 seconds, giving us a
speedup of more than 16$\times$. We are still far away from the ideal
ratio of 20$\times$ (we are using 20 cores), since some provers are
allocating a lot of memory and time spent in system calls is not
accounted for in the total observed time. However, a ratio of
16$\times$ is already a significant improvement for our day-to-day
experiments.

>>>>

The purpose of the following experiments is to compare the various
deployments, namely sequential, cores and network.
For this comparison to be fair, all
computations are performed on the same machine, a 8 cores Intel Xeon
3.2 GHz running Debian Linux. The sequential implementation uses a
single core. The multi-core implementation uses up to 8 cores of
the machine. The network implementation uses 8 workers running locally and
a master running on a remote machine (which incurs communication cost).

@@

The following table shows execution times for various values of $N$
and our three different implementations: \of{Sequential}, \of{Cores}, and
\of{Network}. The purpose of this experiment is to measure the speedup
w.r.t. the sequential implementation.

@@

Here we demonstrate the potential of our library for our application
needs as mentioned in the introduction. 
We consider 80 challenging verification conditions
(VC) obtained from the Why platform~\cite{filliatre07cav}.  Each
VC is stored in a file, which is accessible over
NFS. The purpose of the experiment is to check the validity of each VC
using several automated provers (namely Alt-Ergo, Simplify, Z3 and CVC3).

The master program proceeds by reading the file names, turning them
into tasks by multiplying them by the number of provers, resulting in
320 tasks in total.
Each worker in turn invokes the given prover on the given file, within
a timeout limit of 1 minute.
Each task completes with one of the four possible outcomes: \emph{valid},
\emph{unknown} (depending on
whether the VC is valid or undecided by the prover), 
\emph{timeout} and \emph{failure}.
The result of each computation is a pair denoting the status and the
time spent in the prover call. The master collects these results and
sums up the timings for each prover and each possible status.

Our computing
infrastructure for this experiment consists of 3 machines with 4, 8 and 8 cores
respectively. 
The figure below shows the total time in minutes spent by each prover
for each possible outcome.
\begin{center}
  \begin{tabular}{|r||r|r|r|r|}
    \hline
    prover   & valid & unknown & timeout & failure
    \\\hline\hline
    Alt-ergo & 406.0 & 3.0   &  11400.0 & 0.0       
    \\\hline
    Simplify &  0.5   & 0.4   &  1200.0 & 222.0   
    \\\hline
    Z3       & 80.7   & 0.0   &  1800.0 & 1695.0   
    \\\hline
    CVC3     & 303.0  & 82.7  &  4200.0 & 659.0   
    \\\hline
  \end{tabular}
\end{center}
These figures sum up to more than 6 hours if provers were executed
sequentially. However, using our library and our 3-machine
infrastructure, it completes in 22 minutes and 37 seconds, giving us a
speedup of more than 16$\times$. We are still far away from the ideal
ratio of 20$\times$ (we are using 20 cores), since some provers are
allocating a lot of memory and time spent in system calls is not
accounted for in the total observed time. However, a ratio of
16$\times$ is already a significant improvement for our day-to-day
experiments.
